# BI Checklists {#BI}


## BI HNQIS Malaria 

    
>__Checklist id__: HputaDb8ojM   | __Server__: https://staging.psi-mis.org/ | __user__: BIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[10]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[10]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'HputaDb8ojM', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'HputaDb8ojM', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BI HNQIS Planning Familial: Counseling 

    
>__Checklist id__: tyFuZhWK6AE   | __Server__: https://staging.psi-mis.org/ | __user__: BIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[11]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[11]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'tyFuZhWK6AE', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'tyFuZhWK6AE', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BI HNQIS Planning Familial: Méthodes à courte durée d' action 

    
>__Checklist id__: J8EwWTid1Dw   | __Server__: https://staging.psi-mis.org/ | __user__: BIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[12]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[12]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'J8EwWTid1Dw', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'J8EwWTid1Dw', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BI HNQIS Planning Familial: Méthodes à longue durée d' action 

    
>__Checklist id__: ldgWKjPvtGW   | __Server__: https://staging.psi-mis.org/ | __user__: BIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[13]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[13]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ldgWKjPvtGW', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ldgWKjPvtGW', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BI HNQIS Soins Après Avortement 

    
>__Checklist id__: SABinOLSbE1   | __Server__: https://staging.psi-mis.org/ | __user__: BIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[14]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[14]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'SABinOLSbE1', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'SABinOLSbE1', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BI HNQIS VIH 

    
>__Checklist id__: d1pKqtOYEhp   | __Server__: https://staging.psi-mis.org/ | __user__: BIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[15]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[15]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'd1pKqtOYEhp', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'd1pKqtOYEhp', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
