# BJ Checklists {#BJ}


## BJ HNQIS Cancer du Col utérin 

    
>__Checklist id__: EkMCYNauC0b   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[16]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[16]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'EkMCYNauC0b', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'EkMCYNauC0b', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Client Based Record Management (CBRM) 

    
>__Checklist id__: ORkXVG6k6Gv   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[17]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[17]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ORkXVG6k6Gv', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ORkXVG6k6Gv', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Hypertension 

    
>__Checklist id__: JgZRohvEyzX   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[18]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[18]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'JgZRohvEyzX', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'JgZRohvEyzX', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Paludisme 

    
>__Checklist id__: AG4r0hFjYSf   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[19]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[19]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'AG4r0hFjYSf', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'AG4r0hFjYSf', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Planning Familial: Counseling 

    
>__Checklist id__: XUIbJRb5ukK   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[20]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[20]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'XUIbJRb5ukK', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'XUIbJRb5ukK', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Planning Familial: Méthodes à courte durée d' action 

    
>__Checklist id__: MBWZQOzjOsN   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[21]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[21]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'MBWZQOzjOsN', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'MBWZQOzjOsN', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Planning Familial: Méthodes à longue durée d' action 

    
>__Checklist id__: fTF0GCG7cAi   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[22]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[22]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'fTF0GCG7cAi', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'fTF0GCG7cAi', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Prise en charge intégrée des maladies infantiles 

    
>__Checklist id__: L5wkxFhp6Hy   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[23]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[23]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'L5wkxFhp6Hy', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'L5wkxFhp6Hy', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Réanimation du nouveau-né 

    
>__Checklist id__: dVa56rKz7ej   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[24]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[24]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'dVa56rKz7ej', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'dVa56rKz7ej', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Santé maternelle et néonatale 

    
>__Checklist id__: VMThZpXBN00   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[25]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[25]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'VMThZpXBN00', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'VMThZpXBN00', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Soins Après Avortement 

    
>__Checklist id__: u74KapLT6hp   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[26]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[26]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'u74KapLT6hp', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'u74KapLT6hp', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS VIH 

    
>__Checklist id__: Ixek808rTXf   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[27]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[27]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Ixek808rTXf', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Ixek808rTXf', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## BJ HNQIS Évaluation de l'environnement de travail 

    
>__Checklist id__: UiUwMpenqKH   | __Server__: https://staging.psi-mis.org/ | __user__: BJdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[28]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[28]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'UiUwMpenqKH', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'UiUwMpenqKH', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
