# CM Checklists {#CM}


## CM HNQIS Cancer du Col utérin 

    
>__Checklist id__: dVe2uUnZoBX   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[33]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[33]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'dVe2uUnZoBX', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'dVe2uUnZoBX', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Client Based Record Management (CBRM) 

    
>__Checklist id__: MLh7uIVextF   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[34]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[34]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'MLh7uIVextF', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'MLh7uIVextF', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Hypertension 

    
>__Checklist id__: ERhGVbD3rtV   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[35]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[35]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ERhGVbD3rtV', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ERhGVbD3rtV', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Paludisme 

    
>__Checklist id__: sT2WIr2Hbja   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[36]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[36]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'sT2WIr2Hbja', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'sT2WIr2Hbja', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Planning Familial: Counseling 

    
>__Checklist id__: PyanVWIVC4v   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[37]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[37]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'PyanVWIVC4v', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'PyanVWIVC4v', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Planning Familial: Méthodes à courte durée d' action 

    
>__Checklist id__: vewZ7WoBjZ0   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[38]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[38]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'vewZ7WoBjZ0', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'vewZ7WoBjZ0', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Planning Familial: Méthodes à longue durée d' action 

    
>__Checklist id__: c2kre1kXbXK   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[39]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[39]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'c2kre1kXbXK', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'c2kre1kXbXK', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Prise en charge intégrée des maladies infantiles (PCIME) 

    
>__Checklist id__: PITnNPmGlgF   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[40]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[40]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'PITnNPmGlgF', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'PITnNPmGlgF', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS Soins Après Avortement (SAA) 

    
>__Checklist id__: OGr2MVKGTeP   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[41]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[41]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'OGr2MVKGTeP', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'OGr2MVKGTeP', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## CM HNQIS VIH 

    
>__Checklist id__: SRYvVIdib5a   | __Server__: https://staging.psi-mis.org/ | __user__: CMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[42]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[42]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'SRYvVIdib5a', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'SRYvVIdib5a', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
