# ET Checklists {#ET}


## ET HNQIS Family Planning Counseling 

    
>__Checklist id__: PcBN1NUTygk   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[43]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[43]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'PcBN1NUTygk', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'PcBN1NUTygk', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS Family Planning Long-Acting and Permanent Methods 

    
>__Checklist id__: JO0ffJKhD1o   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[44]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[44]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'JO0ffJKhD1o', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'JO0ffJKhD1o', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS Family Planning Short Acting Methods 

    
>__Checklist id__: T4RPAgBnyv5   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[45]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[45]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'T4RPAgBnyv5', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'T4RPAgBnyv5', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS HIV: Care and Treatment 

    
>__Checklist id__: DrKqNwEoe8g   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[46]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[46]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'DrKqNwEoe8g', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'DrKqNwEoe8g', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS HIV: DIC/Town Management 

    
>__Checklist id__: WtkYsqFAztw   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[47]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[47]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'WtkYsqFAztw', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'WtkYsqFAztw', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS HIV: Gender Based Violence 

    
>__Checklist id__: rh8F5WiCIPX   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[48]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[48]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'rh8F5WiCIPX', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'rh8F5WiCIPX', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS HIV: Laboratory 

    
>__Checklist id__: DXMeTBWW2YU   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[49]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[49]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'DXMeTBWW2YU', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'DXMeTBWW2YU', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS HIV: Testing Services 

    
>__Checklist id__: UiUuYrMT7BO   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[50]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[50]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'UiUuYrMT7BO', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'UiUuYrMT7BO', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ET HNQIS Hypertension 

    
>__Checklist id__: VSCYmZGRRNI   | __Server__: https://staging.psi-mis.org/ | __user__: ETdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[51]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[51]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'VSCYmZGRRNI', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'VSCYmZGRRNI', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
