# JL Checklists {#JL}


## JL HNQIS Birth Spacing: Long Acting and Reversible Methods 

    
>__Checklist id__: NR5jpfT14pQ   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[71]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[71]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'NR5jpfT14pQ', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'NR5jpfT14pQ', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Birth Spacing: Short Acting Methods 

    
>__Checklist id__: aLWu7ffN9D3   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[72]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[72]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'aLWu7ffN9D3', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'aLWu7ffN9D3', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Cervical Cancer: VIA Screening and Cryotherapy 

    
>__Checklist id__: iOWnPrk6ash   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[73]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[73]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'iOWnPrk6ash', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'iOWnPrk6ash', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Health Center - Community Participation & Health Education 

    
>__Checklist id__: SyJ5I8tdrai   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[74]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[74]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'SyJ5I8tdrai', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'SyJ5I8tdrai', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Health Center - Personnel and Infrastructure 

    
>__Checklist id__: wJsY5ofADiA   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[75]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[75]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'wJsY5ofADiA', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'wJsY5ofADiA', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Health Center -  Programs and Health System Support 

    
>__Checklist id__: cv0S9XGfu84   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[76]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[76]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'cv0S9XGfu84', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'cv0S9XGfu84', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Hypertension 

    
>__Checklist id__: w0NRKmKNefC   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[77]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[77]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'w0NRKmKNefC', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'w0NRKmKNefC', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS IMCI 

    
>__Checklist id__: CfhSkwue0ZN   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[78]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[78]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'CfhSkwue0ZN', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'CfhSkwue0ZN', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS LARC and PAC Facility checklist 

    
>__Checklist id__: uJBZWrKARed   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[79]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[79]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'uJBZWrKARed', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'uJBZWrKARed', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Malaria 

    
>__Checklist id__: JrSkR9DMnUe   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[80]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[80]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'JrSkR9DMnUe', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'JrSkR9DMnUe', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Maternal and Newborn Health 

    
>__Checklist id__: pRfOYvWhdsm   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[81]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[81]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'pRfOYvWhdsm', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'pRfOYvWhdsm', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Post Abortion Care 

    
>__Checklist id__: uSUB6tOflGi   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[82]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[82]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'uSUB6tOflGi', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'uSUB6tOflGi', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Regional Hospital - Community Participation & Health Education 

    
>__Checklist id__: D8TwwcgS20I   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[83]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[83]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'D8TwwcgS20I', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'D8TwwcgS20I', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Regional Hospital -  Personnel and Infrastructure 

    
>__Checklist id__: JlNfoVcPv2y   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[84]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[84]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'JlNfoVcPv2y', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'JlNfoVcPv2y', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Regional Hospital - Programs and Health System Support 

    
>__Checklist id__: Pfs7m4vI67d   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[85]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[85]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Pfs7m4vI67d', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Pfs7m4vI67d', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## JL HNQIS Sexually Transmitted Infections 

    
>__Checklist id__: Hp7pUz7skOy   | __Server__: https://sm-dev.hnqis.org/ | __user__: JLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[86]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[86]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Hp7pUz7skOy', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Hp7pUz7skOy', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
