# KE Checklists {#KE}


## KE HNQIS Cervical Cancer: Screening and Cryotherapy 

    
>__Checklist id__: ggxhuvMBtxj   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'ggxhuvMBtxj', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'ggxhuvMBtxj', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Family Planning 

    
>__Checklist id__: MHadckkbMut   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'MHadckkbMut', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'MHadckkbMut', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Family Planning Counseling 

    
>__Checklist id__: mZ0zJcGODwD   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'mZ0zJcGODwD', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'mZ0zJcGODwD', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Family Planning Long-Acting and Permanent Methods 

    
>__Checklist id__: Qt74wJNHTAS   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'Qt74wJNHTAS', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'Qt74wJNHTAS', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Family Planning Short-Acting Methods 

    
>__Checklist id__: qb6IfcDal3r   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'qb6IfcDal3r', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'qb6IfcDal3r', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS HIV 

    
>__Checklist id__: XRqyZbWDgWl   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'XRqyZbWDgWl', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'XRqyZbWDgWl', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Hypertension 

    
>__Checklist id__: u6pCofOY3O7   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'u6pCofOY3O7', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'u6pCofOY3O7', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS IMCI 

    
>__Checklist id__: Wps8E2P8P9S   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'Wps8E2P8P9S', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'Wps8E2P8P9S', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Maternal and Newborn Health 

    
>__Checklist id__: Emzrjjdcfcq   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'Emzrjjdcfcq', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'Emzrjjdcfcq', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Newborn Resuscitation 

    
>__Checklist id__: viBtnUfo7Wk   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'viBtnUfo7Wk', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'viBtnUfo7Wk', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KE HNQIS Work Environment Assessment 

    
>__Checklist id__: TPW9xYrV8i8   | __Server__: https://staging.psi-mis.org/ | __user__: KEdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'TPW9xYrV8i8', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'TPW9xYrV8i8', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```
