# KH Checklists {#KH}


## KH HNQIS Cervical Cancer 

    
>__Checklist id__: qk4UNDJZllE   | __Server__: https://staging.psi-mis.org/ | __user__: KHdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'qk4UNDJZllE', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'qk4UNDJZllE', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KH HNQIS Family Planning Counseling 

    
>__Checklist id__: JmF4SObYwij   | __Server__: https://staging.psi-mis.org/ | __user__: KHdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'JmF4SObYwij', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'JmF4SObYwij', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KH HNQIS Family Planning Long Acting and Permanent Methods 

    
>__Checklist id__: KZl5EuKoerI   | __Server__: https://staging.psi-mis.org/ | __user__: KHdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'KZl5EuKoerI', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'KZl5EuKoerI', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KH HNQIS Family Planning Short Acting Methods 

    
>__Checklist id__: EXEioXna1Uy   | __Server__: https://staging.psi-mis.org/ | __user__: KHdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'EXEioXna1Uy', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'EXEioXna1Uy', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KH HNQIS IMCI 

    
>__Checklist id__: EGTqRTg1ezx   | __Server__: https://staging.psi-mis.org/ | __user__: KHdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'EGTqRTg1ezx', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'EGTqRTg1ezx', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KH HNQIS Malaria 

    
>__Checklist id__: dkWoeeThogR   | __Server__: https://staging.psi-mis.org/ | __user__: KHdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'dkWoeeThogR', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'dkWoeeThogR', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## KH HNQIS Work Environment Assessment 

    
>__Checklist id__: rY1HUcYhhrX   | __Server__: https://staging.psi-mis.org/ | __user__: KHdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'rY1HUcYhhrX', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'rY1HUcYhhrX', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```
