# LA Checklists {#LA}


## LA HNQIS Client Based Record Management (CBRM) 

    
>__Checklist id__: u9E7k90NnmA   | __Server__: https://staging.psi-mis.org/ | __user__: LAdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'u9E7k90NnmA', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'u9E7k90NnmA', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## LA HNQIS Family Planning Counseling 

    
>__Checklist id__: PQkcqGPQDts   | __Server__: https://staging.psi-mis.org/ | __user__: LAdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'PQkcqGPQDts', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'PQkcqGPQDts', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## LA HNQIS Family Planning Long Acting Methods 

    
>__Checklist id__: fgkzqgrcmni   | __Server__: https://staging.psi-mis.org/ | __user__: LAdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'fgkzqgrcmni', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'fgkzqgrcmni', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## LA HNQIS Family Planning Short-Acting Methods 

    
>__Checklist id__: BMX7C2Q59PI   | __Server__: https://staging.psi-mis.org/ | __user__: LAdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'BMX7C2Q59PI', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'BMX7C2Q59PI', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## LA HNQIS Malaria 

    
>__Checklist id__: zpKPn0qReLM   | __Server__: https://staging.psi-mis.org/ | __user__: LAdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'zpKPn0qReLM', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'zpKPn0qReLM', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## LA HNQIS Post Abortion Care 

    
>__Checklist id__: X8rCOBhQHGi   | __Server__: https://staging.psi-mis.org/ | __user__: LAdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'X8rCOBhQHGi', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'X8rCOBhQHGi', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```
