# MG Checklists {#MG}


## MG HNQIS Cancer du Col utérin 

    
>__Checklist id__: Qey5spqS4oM   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[111]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[111]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Qey5spqS4oM', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Qey5spqS4oM', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Client Based Record Management (CBRM) 

    
>__Checklist id__: CRgGAnqbAMy   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[112]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[112]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'CRgGAnqbAMy', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'CRgGAnqbAMy', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Infections sexuellement transmissibles (IST) 

    
>__Checklist id__: kBNpWmAVskk   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[113]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[113]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'kBNpWmAVskk', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'kBNpWmAVskk', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Infections sexuellement transmissibles v1 

    
>__Checklist id__: wQwb3cXciTZ   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[114]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[114]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'wQwb3cXciTZ', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'wQwb3cXciTZ', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Paludisme 

    
>__Checklist id__: URUk0A6cj7n   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[115]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[115]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'URUk0A6cj7n', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'URUk0A6cj7n', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS PF: Counseling 

    
>__Checklist id__: aZhzaYGKy0P   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[116]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[116]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'aZhzaYGKy0P', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'aZhzaYGKy0P', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS PF: Méthodes à courte durée d' action 

    
>__Checklist id__: ykp7gFN9Q1z   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[117]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[117]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ykp7gFN9Q1z', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ykp7gFN9Q1z', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS PF: Méthodes à longue durée d' action 

    
>__Checklist id__: iWqPydeqMSX   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[118]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[118]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'iWqPydeqMSX', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'iWqPydeqMSX', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Planification familiale v1 

    
>__Checklist id__: KbCEO01QVRa   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[119]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[119]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'KbCEO01QVRa', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'KbCEO01QVRa', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Santé Maternelle et Néonatal 

    
>__Checklist id__: qUrSPPhi1CV   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[120]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[120]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'qUrSPPhi1CV', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'qUrSPPhi1CV', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Soins Après Avortement 

    
>__Checklist id__: dnX1kxWWARK   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[121]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[121]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'dnX1kxWWARK', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'dnX1kxWWARK', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Survie de l'enfant 

    
>__Checklist id__: AwJSDPNmaz3   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[122]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[122]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'AwJSDPNmaz3', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'AwJSDPNmaz3', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS VIH 

    
>__Checklist id__: E0Azws3ZZ3e   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[123]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[123]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'E0Azws3ZZ3e', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'E0Azws3ZZ3e', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MG HNQIS Évaluation de l'environnement de travail 

    
>__Checklist id__: cyqfuguJW6C   | __Server__: https://staging.psi-mis.org/ | __user__: MGdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[124]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[124]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'cyqfuguJW6C', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'cyqfuguJW6C', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
