# ML Checklists {#ML}


## ML HNQIS Cancer du Col 

    
>__Checklist id__: ut7nkYZUTLP   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[125]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[125]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ut7nkYZUTLP', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ut7nkYZUTLP', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ML HNQIS Choix éclairé 

    
>__Checklist id__: PE0Dx2KwvOL   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[126]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[126]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'PE0Dx2KwvOL', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'PE0Dx2KwvOL', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ML HNQIS Client Based Record Management (CBRM) 

    
>__Checklist id__: yTA1y1adJc5   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[127]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[127]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'yTA1y1adJc5', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'yTA1y1adJc5', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ML HNQIS PF: Counseling 

    
>__Checklist id__: Jaor9wzrAmi   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[128]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[128]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Jaor9wzrAmi', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Jaor9wzrAmi', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ML HNQIS PF: Méthodes à longue durée d' action 

    
>__Checklist id__: jDvffOBtPxu   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[129]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[129]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'jDvffOBtPxu', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'jDvffOBtPxu', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ML HNQIS Planification familiale v1 

    
>__Checklist id__: HO9DrFSHoXQ   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[130]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[130]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'HO9DrFSHoXQ', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'HO9DrFSHoXQ', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ML HNQIS Soins de post-avortement 

    
>__Checklist id__: cR1kBY3Ak0o   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[131]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[131]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'cR1kBY3Ak0o', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'cR1kBY3Ak0o', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ML HNQIS Évaluation de l'environnement de travail 

    
>__Checklist id__: jncwLCuzYhQ   | __Server__: https://staging.psi-mis.org/ | __user__: MLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[132]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[132]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'jncwLCuzYhQ', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'jncwLCuzYhQ', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
