# MM Checklists {#MM}


## MM HNQIS Family Planning Counseling 

    
>__Checklist id__: gB17In9eqk9   | __Server__: https://myanmar.psi-mis.org/ | __user__: MMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[133]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[133]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'gB17In9eqk9', baseurl = 'https://myanmar.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'gB17In9eqk9', baseurl = 'https://myanmar.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MM HNQIS Family Planning Short Acting Methods 

    
>__Checklist id__: oTTkZMBn1ms   | __Server__: https://myanmar.psi-mis.org/ | __user__: MMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[134]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[134]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'oTTkZMBn1ms', baseurl = 'https://myanmar.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'oTTkZMBn1ms', baseurl = 'https://myanmar.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MM HNQIS Malaria 

    
>__Checklist id__: lUGqq3na2wn   | __Server__: https://myanmar.psi-mis.org/ | __user__: MMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[135]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[135]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'lUGqq3na2wn', baseurl = 'https://myanmar.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'lUGqq3na2wn', baseurl = 'https://myanmar.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## MM HNQIS Post Abortion Care 

    
>__Checklist id__: EpxhxdX4RXn   | __Server__: https://myanmar.psi-mis.org/ | __user__: MMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[136]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[136]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'EpxhxdX4RXn', baseurl = 'https://myanmar.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'EpxhxdX4RXn', baseurl = 'https://myanmar.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
