# NE Checklists {#NE}


## NE HNQIS Cancer du Col utérin 

    
>__Checklist id__: hLfZOGLJZ8n   | __Server__: https://staging.psi-mis.org/ | __user__: NEdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[157]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[157]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'hLfZOGLJZ8n', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'hLfZOGLJZ8n', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NE HNQIS Client Based Record Management (CBRM) 

    
>__Checklist id__: iOk4zAwavwi   | __Server__: https://staging.psi-mis.org/ | __user__: NEdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[158]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[158]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'iOk4zAwavwi', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'iOk4zAwavwi', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NE HNQIS PF Counseling 

    
>__Checklist id__: FuSpwxENtqy   | __Server__: https://staging.psi-mis.org/ | __user__: NEdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[159]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[159]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'FuSpwxENtqy', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'FuSpwxENtqy', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NE HNQIS PF Méthodes à courte durée d' action 

    
>__Checklist id__: gbEmZsJnUS3   | __Server__: https://staging.psi-mis.org/ | __user__: NEdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[160]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[160]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'gbEmZsJnUS3', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'gbEmZsJnUS3', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NE HNQIS PF Méthodes à longue durée d' action 

    
>__Checklist id__: pdf238QIIFa   | __Server__: https://staging.psi-mis.org/ | __user__: NEdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[161]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[161]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'pdf238QIIFa', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'pdf238QIIFa', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NE HNQIS Soins Après Avortement (SAA) 

    
>__Checklist id__: XdApD6VCjbQ   | __Server__: https://staging.psi-mis.org/ | __user__: NEdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[162]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[162]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'XdApD6VCjbQ', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'XdApD6VCjbQ', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NE HNQIS Évaluation de l'environnement de travail 

    
>__Checklist id__: tgxfuOfntDr   | __Server__: https://staging.psi-mis.org/ | __user__: NEdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[163]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[163]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'tgxfuOfntDr', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'tgxfuOfntDr', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
