# NG Checklists {#NG}


## NG HNQIS Client Based Record Management v2 

    
>__Checklist id__: ehKlxTM0nT6   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'ehKlxTM0nT6', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'ehKlxTM0nT6', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NG HNQIS Data Quality Improvement v2 

    
>__Checklist id__: OPKYLFArvxl   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'OPKYLFArvxl', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'OPKYLFArvxl', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NG HNQIS Family Planning: Counseling v2 

    
>__Checklist id__: bmzBKZofUSJ   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'bmzBKZofUSJ', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'bmzBKZofUSJ', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NG HNQIS Family Planning: Long Acting and Permanent Methods v2 

    
>__Checklist id__: DkUpNm7OJye   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'DkUpNm7OJye', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'DkUpNm7OJye', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NG HNQIS Family Planning: Short Acting Methods v2 

    
>__Checklist id__: JKzozIYnMjp   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'JKzozIYnMjp', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'JKzozIYnMjp', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NG HNQIS Post-Abortion Care v2 

    
>__Checklist id__: r1QYcr5LNoY   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'r1QYcr5LNoY', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'r1QYcr5LNoY', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NG HNQIS Sexually Transmitted Infections v3 

    
>__Checklist id__: VK1sGTcacST   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'VK1sGTcacST', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'VK1sGTcacST', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NG HNQIS Work Environment Assessment v2 

    
>__Checklist id__: DESKxhzaTOW   | __Server__: https://staging.psi-mis.org/ | __user__: NGdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'DESKxhzaTOW', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'DESKxhzaTOW', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```
