# NI Checklists {#NI}


## NI HNQIS Atención posterior al aborto (APA) 

    
>__Checklist id__: bHs2qG1EvNV   | __Server__: https://staging.psi-mis.org/ | __user__: NIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[172]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[172]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'bHs2qG1EvNV', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'bHs2qG1EvNV', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NI HNQIS Manejo de Registros basados en el cliente (CBRM) 

    
>__Checklist id__: Ryyfqnx9Cgg   | __Server__: https://staging.psi-mis.org/ | __user__: NIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[173]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[173]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Ryyfqnx9Cgg', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Ryyfqnx9Cgg', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NI HNQIS PF: Asesoría 

    
>__Checklist id__: g7cV8cVtb0p   | __Server__: https://staging.psi-mis.org/ | __user__: NIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[174]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[174]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'g7cV8cVtb0p', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'g7cV8cVtb0p', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## NI HNQIS PF: Métodos de acción prolongada y permanente 

    
>__Checklist id__: VCKsofNTb08   | __Server__: https://staging.psi-mis.org/ | __user__: NIdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[175]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[175]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'VCKsofNTb08', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'VCKsofNTb08', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
