# NP Checklists {#NP}


## NP HNQIS AYP FP: Short Acting Methods 

    
>__Checklist id__: yjFKqnDHZCi   | __Server__: https://staging.psi-mis.org/ | __user__: NPdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'yjFKqnDHZCi', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'yjFKqnDHZCi', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NP HNQIS Family Planning Counseling 

    
>__Checklist id__: pfeZZb5Bstw   | __Server__: https://staging.psi-mis.org/ | __user__: NPdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'pfeZZb5Bstw', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'pfeZZb5Bstw', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NP HNQIS Family Planning Long-Acting and Permanent Methods 

    
>__Checklist id__: gJS9q7FQWQy   | __Server__: https://staging.psi-mis.org/ | __user__: NPdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'gJS9q7FQWQy', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'gJS9q7FQWQy', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NP HNQIS Health Facility Checklists 

    
>__Checklist id__: bsxOnEn4S1q   | __Server__: https://staging.psi-mis.org/ | __user__: NPdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'bsxOnEn4S1q', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'bsxOnEn4S1q', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## NP HNQIS Post Abortion Care 

    
>__Checklist id__: lcNysIeOLR7   | __Server__: https://staging.psi-mis.org/ | __user__: NPdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'lcNysIeOLR7', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'lcNysIeOLR7', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```
