# PL Checklists {#PL}


## PL HNQIS Birth Spacing: Counseling 

    
>__Checklist id__: aVtpoPviqmd   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[181]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[181]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'aVtpoPviqmd', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'aVtpoPviqmd', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Birth Spacing: Long Acting and Reversible Methods 

    
>__Checklist id__: xF3HdsquxQt   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[182]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[182]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'xF3HdsquxQt', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'xF3HdsquxQt', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Birth spacing: Short Acting Methods 

    
>__Checklist id__: A9tZ2zfj59l   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[183]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[183]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'A9tZ2zfj59l', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'A9tZ2zfj59l', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Cervical Cancer: VIA Screening and Cryotherapy 

    
>__Checklist id__: FA6ms2dQ6AI   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[184]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[184]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'FA6ms2dQ6AI', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'FA6ms2dQ6AI', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Health Center - Community Participation & Health Education 

    
>__Checklist id__: h5pntzxCala   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[185]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[185]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'h5pntzxCala', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'h5pntzxCala', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Health Center - Personnel and Infrastructure 

    
>__Checklist id__: K2VOOlL46Dn   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[186]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[186]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'K2VOOlL46Dn', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'K2VOOlL46Dn', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Health Center -  Programs and Health System Support 

    
>__Checklist id__: SAzzot0NY4B   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[187]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[187]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'SAzzot0NY4B', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'SAzzot0NY4B', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Hypertension 

    
>__Checklist id__: uy0Mpc0bbEH   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[188]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[188]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'uy0Mpc0bbEH', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'uy0Mpc0bbEH', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS IMCI 

    
>__Checklist id__: ktHHTvRAcSe   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[189]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[189]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ktHHTvRAcSe', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ktHHTvRAcSe', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS LARC and PAC Facility checklist 

    
>__Checklist id__: O56rdLHqSZU   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[190]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[190]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'O56rdLHqSZU', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'O56rdLHqSZU', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Malaria 

    
>__Checklist id__: RaxNeOA7FVc   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[191]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[191]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'RaxNeOA7FVc', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'RaxNeOA7FVc', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Maternal and Newborn Health 

    
>__Checklist id__: ye9UW4gSlUK   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[192]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[192]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ye9UW4gSlUK', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ye9UW4gSlUK', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Post Abortion Care 

    
>__Checklist id__: eRVhEi818Nn   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[193]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[193]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'eRVhEi818Nn', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'eRVhEi818Nn', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Regional Hospital - Community Participation & Health Education 

    
>__Checklist id__: QDDbt33vRA9   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[194]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[194]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'QDDbt33vRA9', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'QDDbt33vRA9', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Regional Hospital -  Personnel and Infrastructure 

    
>__Checklist id__: h6LVv9i19tp   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[195]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[195]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'h6LVv9i19tp', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'h6LVv9i19tp', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Regional Hospital - Programs and Health System Support 

    
>__Checklist id__: cQOe8ypt12l   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[196]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[196]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'cQOe8ypt12l', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'cQOe8ypt12l', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## PL HNQIS Sexually Transmitted Infections 

    
>__Checklist id__: OtzqRD9k13U   | __Server__: https://sm-dev.hnqis.org/ | __user__: PLdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[197]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[197]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'OtzqRD9k13U', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'OtzqRD9k13U', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
