# SM Checklists {#SM}


## SM HNQIS Birth Spacing Long Acting and Reversible Methods 

    
>__Checklist id__: Ga7Fi2lPd8v   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[198]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[198]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Ga7Fi2lPd8v', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Ga7Fi2lPd8v', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Birth Spacing Short Acting Methods 

    
>__Checklist id__: gqAV6XNoEv2   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[199]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[199]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'gqAV6XNoEv2', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'gqAV6XNoEv2', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Cervical Cancer VIA Screening and Cryotherapy 

    
>__Checklist id__: NNshJ24SbZT   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[200]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[200]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'NNshJ24SbZT', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'NNshJ24SbZT', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Health Center Community Participation and Health Education 

    
>__Checklist id__: H1GyIowZmNa   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[201]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[201]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'H1GyIowZmNa', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'H1GyIowZmNa', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Health Center Personnel and Infrastructure 

    
>__Checklist id__: XPeirPFgA77   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[202]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[202]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'XPeirPFgA77', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'XPeirPFgA77', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Health Center Programs and Health System Support 

    
>__Checklist id__: qm5zqVuy8XN   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[203]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[203]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'qm5zqVuy8XN', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'qm5zqVuy8XN', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Hypertension 

    
>__Checklist id__: BGjaWMpa43H   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[204]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[204]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'BGjaWMpa43H', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'BGjaWMpa43H', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS IMCI 

    
>__Checklist id__: Lv6JwtgtFs9   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[205]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[205]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Lv6JwtgtFs9', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Lv6JwtgtFs9', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS LARC and PAC Facility checklist 

    
>__Checklist id__: r2csrD2gvg8   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[206]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[206]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'r2csrD2gvg8', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'r2csrD2gvg8', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Malaria 

    
>__Checklist id__: Kx9HbYw62bM   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[207]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[207]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'Kx9HbYw62bM', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'Kx9HbYw62bM', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Maternal and Newborn Health 

    
>__Checklist id__: jKgKOUlFl36   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[208]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[208]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'jKgKOUlFl36', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'jKgKOUlFl36', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Post Abortion Care 

    
>__Checklist id__: s3uO1m16w5j   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[209]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[209]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 's3uO1m16w5j', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 's3uO1m16w5j', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Regional Hospital Community Participation and Health Education 

    
>__Checklist id__: GV4XUY8UakS   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[210]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[210]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'GV4XUY8UakS', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'GV4XUY8UakS', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Regional Hospital Personnel and Infrastructure 

    
>__Checklist id__: ZWm96p54HYQ   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[211]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[211]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ZWm96p54HYQ', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ZWm96p54HYQ', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Regional Hospital Programs and Health System Support 

    
>__Checklist id__: aDv6SIIA3He   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[212]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[212]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'aDv6SIIA3He', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'aDv6SIIA3He', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SM HNQIS Sexually Transmitted Infections 

    
>__Checklist id__: WHqSECHTMs4   | __Server__: https://sm-dev.hnqis.org/ | __user__: SMdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[213]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[213]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'WHqSECHTMs4', baseurl = 'https://sm-dev.hnqis.org/')
  

  # Detail
   generate_kable_2(form_id = 'WHqSECHTMs4', baseurl = 'https://sm-dev.hnqis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
