# SV Checklists {#SV}


## SV HNQIS Atención posterior al aborto (APA) 

    
>__Checklist id__: rtoWzmt9Wqy   | __Server__: https://staging.psi-mis.org/ | __user__: SVdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[214]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[214]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'rtoWzmt9Wqy', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'rtoWzmt9Wqy', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SV HNQIS Cáncer cervical 

    
>__Checklist id__: pkltIZaWWgc   | __Server__: https://staging.psi-mis.org/ | __user__: SVdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[215]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[215]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'pkltIZaWWgc', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'pkltIZaWWgc', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SV HNQIS Infecciones de Transmisión Sexual 

    
>__Checklist id__: WPEevrl1h2Z   | __Server__: https://staging.psi-mis.org/ | __user__: SVdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[216]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[216]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'WPEevrl1h2Z', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'WPEevrl1h2Z', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SV HNQIS Manejo de Registros basados en el cliente (CBRM) 

    
>__Checklist id__: XvNLKPRkuTT   | __Server__: https://staging.psi-mis.org/ | __user__: SVdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[217]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[217]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'XvNLKPRkuTT', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'XvNLKPRkuTT', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SV HNQIS PF: Asesoría 

    
>__Checklist id__: AEypSk1KjEV   | __Server__: https://staging.psi-mis.org/ | __user__: SVdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[218]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[218]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'AEypSk1KjEV', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'AEypSk1KjEV', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SV HNQIS PF: Métodos acción corta 

    
>__Checklist id__: z0NnAjFaK6h   | __Server__: https://staging.psi-mis.org/ | __user__: SVdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[219]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[219]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'z0NnAjFaK6h', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'z0NnAjFaK6h', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## SV HNQIS PF: Métodos de acción prolongada y permanente 

    
>__Checklist id__: mR5vaQAArgA   | __Server__: https://staging.psi-mis.org/ | __user__: SVdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[220]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[220]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'mR5vaQAArgA', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'mR5vaQAArgA', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
