# TZ Checklists {#TZ}


## TZ HNQIS - Post Abortion Care 

    
>__Checklist id__: XEFrBroRgzj   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'XEFrBroRgzj', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'XEFrBroRgzj', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS Cervical Cancer 

    
>__Checklist id__: fouXJvFOJ59   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'fouXJvFOJ59', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'fouXJvFOJ59', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS Family Planning 

    
>__Checklist id__: cTaNilIaaTJ   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'cTaNilIaaTJ', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'cTaNilIaaTJ', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS Family Planning Counseling 

    
>__Checklist id__: z44BIK8op1w   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'z44BIK8op1w', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'z44BIK8op1w', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS Family Planning: Long Acting and Permanent Methods 

    
>__Checklist id__: hE7E23silMJ   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'hE7E23silMJ', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'hE7E23silMJ', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS IMCI 

    
>__Checklist id__: t6yF3GiOykF   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 't6yF3GiOykF', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 't6yF3GiOykF', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS IPC Supervision Form 

    
>__Checklist id__: FhukhATo7Dq   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'FhukhATo7Dq', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'FhukhATo7Dq', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS Malaria 

    
>__Checklist id__: VlGjMyib5GX   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'VlGjMyib5GX', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'VlGjMyib5GX', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS Work Environment Assessment 

    
>__Checklist id__: G58SSNpAgSb   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'G58SSNpAgSb', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'G58SSNpAgSb', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## TZ HNQIS Work Environment Assessment v1 

    
>__Checklist id__: oYQA2XedUNq   | __Server__: https://staging.psi-mis.org/ | __user__: TZdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'oYQA2XedUNq', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'oYQA2XedUNq', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```
