# VN Checklists {#VN}


## VN HNQIS Hypertension 

    
>__Checklist id__: dEzEakMxEv3   | __Server__: https://staging.psi-mis.org/ | __user__: VNdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[247]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[247]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'dEzEakMxEv3', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'dEzEakMxEv3', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## VN HNQIS Malaria 

    
>__Checklist id__: SPS5p0x0Wwo   | __Server__: https://staging.psi-mis.org/ | __user__: VNdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[248]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[248]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'SPS5p0x0Wwo', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'SPS5p0x0Wwo', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## VN HNQIS Malaria: pharmacies and non health outlets 

    
>__Checklist id__: qD8i8zk542M   | __Server__: https://staging.psi-mis.org/ | __user__: VNdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[249]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[249]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'qD8i8zk542M', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'qD8i8zk542M', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
