# ZA Checklists {#ZA}


## ZA HNQIS HIV HTS Counseling and Testing Sit-in Supervision tool 

    
>__Checklist id__: sVitOIK8xZb   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[250]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[250]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'sVitOIK8xZb', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'sVitOIK8xZb', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS HIV Site Assessment Form 

    
>__Checklist id__: ExKwKgYhXP4   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[251]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[251]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ExKwKgYhXP4', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ExKwKgYhXP4', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS HIV SPI-RT Checklist 

    
>__Checklist id__: gPrKFKyfC3v   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[252]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[252]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'gPrKFKyfC3v', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'gPrKFKyfC3v', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS HIVSS Quality Assessment Tool 

    
>__Checklist id__: IEfy68UOBLF   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[253]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[253]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'IEfy68UOBLF', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'IEfy68UOBLF', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS VMMC Client Record Review 

    
>__Checklist id__: ApfcDIK0TZX   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[254]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[254]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'ApfcDIK0TZX', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'ApfcDIK0TZX', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS VMMC Communications to Clients Program 

    
>__Checklist id__: HDIc6HX8ZEb   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[255]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[255]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'HDIc6HX8ZEb', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'HDIc6HX8ZEb', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS VMMC Facilities, Supplies, Equipment, and  Emergency Management 

    
>__Checklist id__: LyKPFwx6DLk   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[256]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[256]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'LyKPFwx6DLk', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'LyKPFwx6DLk', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS VMMC SOPs, Guidelines, Policies and Job Aids and Adequacy of Staffing 

    
>__Checklist id__: OOSYzE6QWds   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[257]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[257]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'OOSYzE6QWds', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'OOSYzE6QWds', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```

## ZA HNQIS VMMC Surgical Equipment and Procedures 

    
>__Checklist id__: i2VZbwoJNkK   | __Server__: http://sfhza.psi-mis.org/ | __user__: ZAdemo1 


    
- Does this checklist have any __mandatory__ question? `r scoring_forms[[258]] %>% gen_test_for_questions(., is_mandatory = T)`
    
- Does this checklist have any __non mandatory__ question? `r scoring_forms[[258]] %>% gen_test_for_questions(., is_mandatory = F)`

```{r, echo=F}

  # summary
  generate_kable_1(form_id = 'i2VZbwoJNkK', baseurl = 'http://sfhza.psi-mis.org/')
  

  # Detail
   generate_kable_2(form_id = 'i2VZbwoJNkK', baseurl = 'http://sfhza.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)


```
