# ZW Checklists {#ZW}


## ZW HNQIS Cervical Cancer 

    
>__Checklist id__: fEq0MH3LIk2   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'fEq0MH3LIk2', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'fEq0MH3LIk2', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS Family Planning Counseling 

    
>__Checklist id__: ucHGfAh00Fe   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'ucHGfAh00Fe', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'ucHGfAh00Fe', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS Family Planning Long Acting Methods 

    
>__Checklist id__: nmJsWtMiSpU   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'nmJsWtMiSpU', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'nmJsWtMiSpU', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS Family Planning Short Acting Methods 

    
>__Checklist id__: wchFlLsSF8H   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'wchFlLsSF8H', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'wchFlLsSF8H', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV ART Nurse Counselor Supervision Tool 

    
>__Checklist id__: ihaZ275KX0j   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'ihaZ275KX0j', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'ihaZ275KX0j', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV Care and Treatment 

    
>__Checklist id__: Oz5VICQFylx   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'Oz5VICQFylx', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'Oz5VICQFylx', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV Gender Based Violence 

    
>__Checklist id__: l65vkKlG6s2   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'l65vkKlG6s2', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'l65vkKlG6s2', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV Index Case Tracing Supervision Tool-Index Nurse Supervision 

    
>__Checklist id__: kNyW7FMaFrh   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'kNyW7FMaFrh', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'kNyW7FMaFrh', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV Laboratory Scientist/Nurse Counselor Tool 

    
>__Checklist id__: INMnvdXUj6B   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'INMnvdXUj6B', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'INMnvdXUj6B', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV New Start Office Assistant/Driver Supervision Tool 

    
>__Checklist id__: BLJwlzBSydD   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'BLJwlzBSydD', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'BLJwlzBSydD', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV New Start Receptionist/Driver Supervision Tool 

    
>__Checklist id__: fZ4WR2WPXlO   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'fZ4WR2WPXlO', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'fZ4WR2WPXlO', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV Testing and Counseling Supervision Tool 

    
>__Checklist id__: Kzfr1s3kkjf   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'Kzfr1s3kkjf', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'Kzfr1s3kkjf', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS HIV Testing and Counselling Site Assessment 

    
>__Checklist id__: Jn35KFbRJT0   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'Jn35KFbRJT0', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'Jn35KFbRJT0', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS Sexually Transmitted Infections v2 

    
>__Checklist id__: BjXg2DLKT20   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'BjXg2DLKT20', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'BjXg2DLKT20', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS STIs v1 

    
>__Checklist id__: BUzCzJM3a78   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'BUzCzJM3a78', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'BUzCzJM3a78', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS VMMC DHE CQI TOOL 

    
>__Checklist id__: eNVyPstiFtO   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'eNVyPstiFtO', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'eNVyPstiFtO', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS VMMC: Client Record Review 

    
>__Checklist id__: woteH2Jwjvp   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'woteH2Jwjvp', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'woteH2Jwjvp', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS VMMC: Communication to Clients 

    
>__Checklist id__: YkE2fPLr6Z9   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'YkE2fPLr6Z9', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'YkE2fPLr6Z9', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS VMMC: Facilities, Supplies, Equipment, and Emergency Management 

    
>__Checklist id__: WhDZb7hSNv9   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'WhDZb7hSNv9', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'WhDZb7hSNv9', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS VMMC: SOPs, Guidelines, Policies, Job Aids and Adequacy of Staffing 

    
>__Checklist id__: zzx27rh50ZN   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'zzx27rh50ZN', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'zzx27rh50ZN', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS VMMC: Surgical Equipment and Procedures, and Prepex Device Procedures 

    
>__Checklist id__: EaEMPVE6y2K   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'EaEMPVE6y2K', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'EaEMPVE6y2K', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```

## ZW HNQIS Work Environment Assessment 

    
>__Checklist id__: qp2e0D239kh   | __Server__: https://staging.psi-mis.org/ | __user__: ZWdemo1 


```{r, echo=F}
  
  # summary
  generate_kable_1(form_id = 'qp2e0D239kh', baseurl = 'https://staging.psi-mis.org/')
  

  # Detail 
   generate_kable_2(form_id = 'qp2e0D239kh', baseurl = 'https://staging.psi-mis.org/', ignore_text = T, ignore_parent = T, ignore_real_or_simulated = T)

   
```
